Supplementary appendix

### 2019-07-24 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@

`r table.x=table.x+1`**Table `r table.x`: Regression analyses – policy presented first of order.**

@@

The following regression tables replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`).

>>>>

In the regression tables below, I report the results of additional robust analyses.

*Table A1* replicates the interaction models in the paper (1.3, 3.2 and 2.3) while restricting the sample to those who saw that policy first before the recycling policy. The directions of the coefficients in these models remain intact. The effect of the real symbols is greater, compared with the full sample (in both policies). This may indicate that the impact of symbols diminishes between the first and the second time participants are exposed to them.

*Table A2* compares between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects' city of residence, and its geographical proximity to the polluting industrial area; (b) Parents for young children. The selection of these two variables is driven by the media coverage of the reports published in 2015-6 regarding the air-pollution in the Haifa Bay. The media reports following the publication of the the statistical data of the Ministry of Health in 2015 mostly highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [e.g. @elroi_website_2015; @raavad_website_2015]. Thereafter, reports of the epidemiological study both emphasized the finding regarding the small heads of babies in Haifa Bay, as well as that areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].

For the first proxi, I selected the three cities/suburbs that are closer to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in all other cities in the Haifa Bay sample (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`). The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`). As for the second proxi, I use a binary variable coded 1 for parents for children under 12 years, and 0 otherwise. However, while I expect parents for young children to be more engaged, that assumption is not supported by differences in self-reported perceived personal relevance. In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.

The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols. The interaction between proximity and the real symbols is positive and significant. As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content. The interaction between parents for young children and the fake symbols is positive and significant.

In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant. However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp. 188-9].

Finally, *Tables A3-A5* replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`). The results of these models latter models do not substantially diverge from the results of the main models.

@@

`r table.x=table.x+1`**Table A`r table.x`: Regression analyses – policy presented first of order.**

@@
